---
output: github_document
always_allow_html: true
---

<!-- README.md is generated from README.Rmd. Please edit that file. -->

# hfsis

hfsis implements variable screening for synchronous, equally spaced
high-frequency regression increments. It provides marginal spot independence
screening (M-SIS) and partial-residual spot iterative screening (PR-SISIS).
M-SIS selects a local window from the marginal correlation vector. PR-SISIS
updates the selected window as the active set grows and computes correlation
columns only when they are required.

## Installation

```r
install.packages(
  "hfsis_0.1.0.tar.gz",
  repos = NULL,
  type = "source"
)
```

## Quick start: M-SIS and PR-SISIS

```{r quick-start, message=FALSE}
library(hfsis)
data(hf_sis_example)

dat <- hf_sis_example$data
x <- as.matrix(dat[hf_sis_example$x_names])
y <- dat[[hf_sis_example$response]]

ctrl <- hfsis_control(
  windows = hf_sis_example$windows,
  truncation = "bipower"
)
inputs <- prepare_hfsis(
  x = x,
  y = y,
  target_index = hf_sis_example$target_index,
  control = ctrl
)

fit_m <- m_sis(
  inputs,
  list_size = 10L
)

fit_pr <- pr_sisis(
  inputs,
  model_cap = 10L,
  block_size = 2L
)

selected_variables(fit_m)
selected_variables(fit_pr)
compare_screens(fit_m, fit_pr)
```

The prepared object stores the common truncated local data and marginal window
summaries. M-SIS uses the marginal-only window selector. PR-SISIS reselects the
window at each update after incorporating the correlation columns associated
with the current active set. Complete PR-SISIS fits provide a full ranking.
Exact score ties use the original column order.

The main diagnostic plots are:

```{r plots, eval=FALSE}
plot(fit_m, type = "scores")
plot(fit_m, type = "window")
plot(fit_pr, type = "path")
plot(compare_screens(fit_m, fit_pr))
```

## Repeated screening

```{r repeated, message=FALSE}
data(hf_sis_panel_example)
panel_fits <- unlist(lapply(hf_sis_panel_example$sessions, function(session) {
  prepared <- prepare_hfsis(
    as.matrix(session[hf_sis_panel_example$x_names]),
    session[[hf_sis_panel_example$response]],
    hf_sis_panel_example$target_index,
    hfsis_control(hf_sis_panel_example$windows)
  )
  list(
    m_sis(prepared, list_size = 5),
    pr_sisis(prepared, model_cap = 5L, block_size = 2L)
  )
}), recursive = FALSE)

frequencies <- selection_frequency(
  panel_fits,
  metadata = hf_sis_panel_example$metadata
)
head(frequencies)
cluster_share(panel_fits, hf_sis_panel_example$metadata)
```

Selection frequency is descriptive empirical recurrence. It is not a support
probability, p-value, or significance measure.

## Input conventions

- Rows are consecutive equally spaced increments or returns, not price levels.
- Columns of x are synchronous candidate covariates; y is the response
  increment.
- target_index is the first increment row in every forward candidate window.
- delta is observation spacing on the normalized time scale and defaults to
  1 / nrow(x).
- Column order is preserved and determines exact-tie resolution.
- Rows are never silently dropped, imputed, or standardized outside the
  correlation normalization defined by the method.

## Scope

Version 0.1.0 assumes synchronous, equally spaced increments and uses forward
local windows. The package does not adjust for asynchronous observations,
market microstructure noise, or price staleness.

## Citation

Please cite Haibin Zhu, “Ultra-high-dimensional spot support screening in
continuous-time regression,” together with hfsis version 0.1.0. The installed
package citation is available through:

```r
citation("hfsis")
```
