---
title: "Method and implementation"
output: html_document
vignette: >
  %\VignetteIndexEntry{Method and implementation}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>")
```

At the target time, the standardized spot quantities obey

$$
r_\tau = R_\tau \theta_\tau.
$$

The support of the marginal vector $r_\tau$ can differ from the regression
support of $\theta_\tau$. Correlated active coordinates with opposing
coefficients may cancel marginally, while an inactive correlated surrogate may
have a large marginal score.

For every candidate forward window, hfsis computes the marginal correlation
vector and the diagonal variance summaries after coordinatewise truncation.
M-SIS selects its window from the marginal vector alone.

PR-SISIS starts from the empty active set. At each update, it compares the
marginal vector together with the correlation columns associated with the
current active set. New columns are computed on demand and cached. The selected
window can therefore change across updates. Partial-residual coefficients are
computed with an ordinary linear solve; a singular active block terminates the
path.

```{r}
library(hfsis)
data(hf_sis_example)
dat <- hf_sis_example$data
inputs <- prepare_hfsis(
  as.matrix(dat[hf_sis_example$x_names]),
  dat[[hf_sis_example$response]],
  hf_sis_example$target_index,
  hfsis_control(
    hf_sis_example$windows,
    threshold_multiplier = 4,
    threshold_exponent = 0.47
  )
)
summary(m_sis(inputs, list_size = 5L))
summary(pr_sisis(inputs, model_cap = 5L, block_size = 2L))
```

The full-sample bipower scale determines the coordinatewise truncation
thresholds. Variance floors are used only during correlation normalization.
