---
title: "Quick start"
output: html_document
vignette: >
  %\VignetteIndexEntry{Quick start}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 7, fig.height = 4)
```

hfsis expects a numeric matrix of synchronous, equally spaced covariate
increments and a numeric response-increment vector. The target index is the
first row used by every forward candidate window.

```{r}
library(hfsis)
data(hf_sis_example)
dat <- hf_sis_example$data
x <- as.matrix(dat[hf_sis_example$x_names])
y <- dat[[hf_sis_example$response]]

control <- hfsis_control(
  windows = hf_sis_example$windows,
  truncation = "bipower"
)
inputs <- prepare_hfsis(x, y, hf_sis_example$target_index, control)
inputs
```

The prepared object stores the common truncated local data and marginal window
summaries. M-SIS uses the marginal-only window selector. PR-SISIS reselects the
window at each update after incorporating the correlation columns associated
with the current active set.

```{r}
m_fit <- m_sis(inputs, list_size = 5)
pr_fit <- pr_sisis(inputs, model_cap = 5L, block_size = 2L)
selected_variables(m_fit)
selected_variables(pr_fit)
screen_ranking(m_fit)
screen_path(pr_fit)
compare_screens(m_fit, pr_fit)
```

Use score, window, and path plots for different diagnostics.

```{r}
plot(m_fit, type = "scores", top = 10)
plot(m_fit, type = "window")
plot(pr_fit, type = "window")
plot(pr_fit, type = "path")
```

Rows with missing or infinite values are rejected rather than dropped or
imputed. Inputs must be increments or returns, not price levels.
