---
title: "Repeated screening"
output: html_document
vignette: >
  %\VignetteIndexEntry{Repeated screening}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", fig.width = 7, fig.height = 8)
```

Fit each session independently, using a stable variable universe and order.

```{r}
library(hfsis)
data(hf_sis_panel_example)

fits <- unlist(lapply(hf_sis_panel_example$sessions, function(dat) {
  prepared <- prepare_hfsis(
    as.matrix(dat[hf_sis_panel_example$x_names]),
    dat[[hf_sis_panel_example$response]],
    hf_sis_panel_example$target_index,
    hfsis_control(hf_sis_panel_example$windows)
  )
  list(
    m_sis(prepared, list_size = 5),
    pr_sisis(prepared, model_cap = 5L, block_size = 2L)
  )
}), recursive = FALSE)

frequency <- selection_frequency(
  fits, metadata = hf_sis_panel_example$metadata
)
frequency[order(frequency$method, -frequency$frequency), ][1:12, ]
shares <- cluster_share(fits, hf_sis_panel_example$metadata)
shares
```

```{r}
plot_selection_frequency(frequency, top = 8, group = "cluster")
plot_cluster_share(shares)
comparison <- compare_screens(fits[[1]], fits[[2]])
plot(comparison)
```

These summaries describe recurrence and composition only. A frequency is not a
support probability or significance measure, and real data do not reveal the
true support.

To adapt this workflow to the public High-Frequency Factor Zoo data, download
the data from https://www.sakethaleti.com/data, form synchronous equally spaced
factor and response returns, preserve a fixed metadata order, and fit each
complete day separately. The package deliberately does not redistribute those
data; users must review their source terms and data quality themselves.
